---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "notes/figures/",
  out.width = "100%",
  dpi=130
)
```

# pictplot

<!-- badges: start -->
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/pictplot)](https://cran.r-project.org/package=pictplot)
[![CRAN_time_from_release](https://www.r-pkg.org/badges/ago/pictplot)](https://cran.r-project.org/package=pictplot)
[![CRAN_latest_release_date](https://www.r-pkg.org/badges/last-release/pictplot)](https://cran.r-project.org/package=pictplot)
[![metacran downloads](https://cranlogs.r-pkg.org/badges/grand-total/pictplot)](https://cran.r-project.org/package=pictplot)
[![license](https://img.shields.io/github/license/mashape/apistatus.svg)](https://choosealicense.com/licenses/mit/)
<!-- badges: end -->

This is an R package that contains a lot of basic image processing functions.

## Dependencies

Mac users need to install XQuartz (https://www.xquartz.org/).

## Installation

This package is currently not available on CRAN. The development version of the package can be installed vie GitHub.

### Installation via GitHub

You can install the development version of the ```pictplot``` package via GitHub, by using the ```devtools``` package.

```{r, eval=FALSE, echo=TRUE}
# install the devtools package
install.packages("devtools")
```

__NOTE:__  
To install a package from GitHub,  
- On Windows, <a href="https://cran.r-project.org/bin/windows/Rtools/">Rtools</a> needs to be installed.  
- On Mac, XCode may be needed to be installed.

After you have installed the required software stated above, install the package as follows:

``` r
# install the pictplot package
devtools::install_github("tsuda16k/pictplot")
```

Then, load the package.

```{r}
library(pictplot)
```
